\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-06 tex/paper.tex
Rewrote access rules

%{{{
\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}
\usepackage{extarrows}
\usepackage{mathpartir}

@@

\subsection{Access rights}
The \textit{a} notation is meant to symbolise an access token, and if \textit{a} exists in the
requested entity of the matrix the corresponding user to that entity has full access to the
corresponding object.

\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        u \in U \text{ can delete } m \in c & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        \forall c \in C, \nexists u \in U & \text{ can delete } f \in c
    \end{split}
\end{equation}

\fix The last one means that no users can delete actual files, probably a bit confusingly written, 
or even wrong?

>>>>

%{{{
\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}
\usepackage{extarrows}
\usepackage{mathpartir}
\usepackage{centernot}

@@

\subsection{Access rights}
The \textit{A[u,c]} notation is symbolising an access token, and if \textit{A[u,c]} exists in
the access matrix \textit{A}, user \textit{u} has full access to the container object \textit{c} and
its children.

\begin{equation}
    \begin{split}
        A[u,c] \in A \Rightarrow & u \text{ can read } c \\
        A[u,c] \in A \land \text{ read-only } \notin c \Rightarrow & u \text{ can write to } c \\
        A[u,c] \in A \land \text{ read-only } \notin c \Rightarrow & u \text{ can delete } c \\
        A[u,c] \in A \land f \in c \centernot\Rightarrow & u \text{ can delete } f 
    \end{split}
\end{equation}
